Reanalysis Step 2: Multiple Imputation

### 2025-08-30 reanalysis-2-multiple_imputation.qmd
50 -> 30

# Set parameters based on mode
if (analysis_mode == "test") {
  n_imputations <- 2
  n_iterations <- 2
} else if (analysis_mode == "final") {
  n_imputations <- 50
  n_iterations <- 20
} else {
  stop("Invalid analysis_mode. Must be 'test' or 'final'")
}

>>>>

# Set parameters based on mode
if (analysis_mode == "test") {
  n_imputations <- 2
  n_iterations <- 2
} else if (analysis_mode == "final") {
  n_imputations <- 30
  n_iterations <- 20
} else {
  stop("Invalid analysis_mode. Must be 'test' or 'final'")
}
